A Meta-analysis of Fungicide Spray Schedules to Minimise Yield Loss from Powdery Mildew in Australian Mungbean

### 2020-08-07 paper/paper.Rmd
Wordsmithing

Considering the November 2019 launch of the mobile app decision support system (DSS) PowderyMildewMBM [@Diggle], which provides a cost benefit analysis to assists growers in their decision "if" and "when" apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
The aim of this meta-analysis was to determine, from a collection of unpublished studies, what spray management scenario provides the greatest yield protection from powdery mildew in Australian mungbean.

>>>>

With the November 2019 launch of the mobile app decision support system (DSS) PowderyMildewMBM [@Diggle], which provides a cost benefit analysis to assists growers in their decision "if" and "when" apply fungicide; a meta-analysis to evaluate and verify the best fungicide spray schedule seemed prudent.
The aim of this meta-analysis was to determine, from a collection of unpublished studies, what spray management scenario provides the greatest yield protection from powdery mildew in Australian mungbean.
